---
title: "HPTN 061 Initial Visit Scoring"
author: "Blaise Albis-Burdige"
date: '`r format(Sys.time(), "%B %d, %Y %r %Z")`'
output:
  html_document:
    highlight: tango
    theme: cerulean
    toc: yes
    toc_depth: 5
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, comment=NA)
```

#Setup
##Imports

```{r}
library(readr)
library(stringr)
library(dplyr)
library(knitr)
library(kableExtra)
library(table1)
library(car)
library(assertthat)

```
##Reading In Dataset
```{r}
hptn <- read_csv('hptn061WideFinalMod.csv')
```

#Demographic Information
## Birthplace given by DEMcount
```{r Birthplace, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest1 <- (hptn$DEMcount_101)




##Replace numeric code with corresponding string

 factorOfInterest1<- recode(factorOfInterest1, 
        "840 = 'USA';581='US Outlying Island';084='Belize';120='Cameroon';124='Canada';132='Cape Verde';192='Cuba';231='Ethiopia';250='France';288='Ghana';384='Ivory Coast';404='Kenya';484='Mexico';504='Morocco';566='Nigeria';686='Senegal';710='South Africa';724='Spain';780='Trinidad and Tobago';388='Other';630='Other';591='Other';800='Other';430='Other';332='Other';276='Other';52='Other';850='Other';716='Other';44='Other';324='Other';32='Other';308='Other';266='Other';214='Other';212='Other';136='Other';else=") 



n <- (table(factorOfInterest1))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Education given by DEMeduc (highest grade completed)
```{r Education, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest2 <- (hptn$DEMeduc_101)



##Replace numeric code with corresponding string

factorOfInterest2<- recode(factorOfInterest2, 
       "1 = '8th grade or equivalent or less';2='Some high school';3='High school graduate or equivalent';4='Vocational/trade/technical school';5='Some college or 2 year degree';6='Finished college';7='Masters or other advanced degree';NA='NA';else=")


n <- (table(factorOfInterest2))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Employment (DEMwork)
```{r Employment, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest4 <- (hptn$DEMwork_101)



##Replace numeric code with corresponding string

factorOfInterest4<- recode(factorOfInterest4, 
       "1 = 'Yes, working full-time';2='yes, working part-time';3='No, unemployed';4='No, retired';5='No, unable to work';NA='NA';else=")

n <- (table(factorOfInterest4))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Yearly Income (DEMincom)
```{r Income, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest3 <- (hptn$DEMincom_101)




##Replace numeric code with corresponding string

factorOfInterest3<- recode(factorOfInterest3, 
       "1 = 'Less than $5,000';2='$5,000-$9,999';3='$10,000-$19,999';4='$20,000-$29,999';5='$30,000-$39,999';6='$40,000-$49,999';7='$50,000-$59,999';8='$60,000-$69,999';9='$70,000-$79,999';10='$80,000 or more';NA='NA';else=")



n <- (table(factorOfInterest3))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Frequency of insufficient income support in the last 6 months  (DEMnomon)
```{r insfIncome, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest5 <- (hptn$DEMnomon_101)



##Replace numeric code with corresponding string

factorOfInterest5<- recode(factorOfInterest5, 
       "1 = 'Never';2='Once in a while';3='Fairly often';4='Very often';NA='NA';else=")


n <- (table(factorOfInterest5))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]


kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Have health coverage?(DEMhcov_101)
```{r HealthCoverage, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest6 <- (hptn$DEMhcov_101)




##Replace numeric code with corresponding string

factorOfInterest6<- recode(factorOfInterest6, 
       "1 = 'Yes';2='No';NA='NA';else=")


n <- (table(factorOfInterest6))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Description of household (DEMhouse_101)
```{r Household, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest7 <- (hptn$DEMhouse_101)





##Replace numeric code with corresponding string

factorOfInterest7<- recode(factorOfInterest7, 
       "1 = 'Living alone';2='Living with a partner or spouse (with or without children)';3='Living with a roommate or roommates (who are not partners)';4='Living with relatives';5='Living with members of my house (such as house ball community)';6='Do not have a stable home';7='Other';NA='NA';")

n <- (table(factorOfInterest7))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Where did you get your most recent HIV test?(ACTSTWH_101)
```{r recentTest, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest8 <- (hptn$ACTSTWH_101)





##Replace numeric code with corresponding string

factorOfInterest8<- recode(factorOfInterest8, 
       "1= 'HIV/AIDS street outreach program/Mobile Unit'; 
2= 'HIV counseling and testing site'; 
3= 'Needle exchange program'; 
4= 'Research site'; 
5= 'Adult HIV/AIDS or infectious disease clinic'; 
6= 'Sexually transmitted disease clinic'; 
7= 'Community health center/public health clinic/free clinic'; 
8= 'Family planning clinic'; 
9= 'Hospital outpatient clinic'; 
10= 'Emergency room'; 
11= 'Drug treatment program'; 
12= 'Private doctors office (including HMO)'; 
13= 'Correctional facility (jail or prison)'; 
14= 'Military'; 
15= 'Home health care'; 
16= 'Other';")




n <- (table(factorOfInterest8))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Why did you choose to get tested for HIV this most recent time?(AC_101)
```{r ReasonForTest, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$AC1_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      " 'SICK'= 'I was sick'; 'NOC,INC'='I did not use a condom when having sex & I was in jail, prison, or juvenile detention center';'NWSO,ADV'=  'I had just started a new relationship & Someone told me to get tested'; 'NOC,OTCR'= 'I did not use a condom when having sex & I was offered testing with other care';
'BRKC'= 'A condom broke'; 
'NOC'= 'I did not use a condom when having sex'; 
'NWSO'= 'I had just started a new relationship'; 
'INJ'= 'I used needles to inject drugs'; 
'ADV'= 'Someone told me to get tested'; 
'DKNW'= 'I did not know I was being tested'; 
'APPT'= 'It was at a routine medical appointment'; 
'PHYS'= 'I had an employee physical'; 
'BLOD'= 'I gave blood'; 
'MILT'= 'I joined the military'; 
'INC'= 'I was in jail, prison, or juvenile detention center'; 
'CLUB'= 'I saw testing at a bar or club'; 
'VAN'= 'I saw a testing program on the street (i.e. mobile van, health fair, etc.)'; 
'PRDE'= 'I saw a testing program at a pride celebration (e.g. gay pride parade, festival)'; 
'SCHL'= 'It was at a testing program in school';
'OTCR'= 'I was offered testing with other care (e.g. STD clinic, ER, community health program)';
'PAID'= 'I was provided money to get tested';'OTH'= 'Other';'NOC,NWSO'= 'I did not use a condom when having sex & I had just started a new relationship';'BRKC,NOC'= 'A condom broke';'NOC,VAN'='A condom broke'; 'NOC,OTH'='A condom broke';'NOC,APPT'='A condom broke';'NOC,ADV'='A condom broke';'NOC,NWSO,ADV'='A condom broke';else=")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Gender Identity: Which of the following word or words do you feel best describes you today? (AC3_101)
```{r genderIdent, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$AC3_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      "'MALE'='Male';'MALE,REAL'='Male & Realness';'MALE,BTCH'='Male & Butch queen';'MALE,OTHB'='Male & Other';'MALE,FMLE'='Male & Female';'MALE,TRNS'='Male & Transsexual';'MALE,GQ'='Male & Genderqueer';'MALE,Feme'='Male & Femme queen';'MALE,REAL,BTCH'='Male & Realness & Butch queen';
      'FMLE'='Female';
      'TRNG'='Transgender';
      'TRNS'='Transsexual'; 
      'GQ'='Genderqueer';
      'REAL'='Realness';
      'BTCH'='Butch queen';
      'FEME'='Femme queen';
      'TRNY'='Trannie';
      'INTER'='Intersex';
      'CRSS'='Crossdresser';
      'OTHB'='Other'; else = 'Some other combo';
      ")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##4-Level Incarceration: Which of the following word or words do you feel best describes you today? (inc4_101)
```{r genderIdent, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$inc4_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      "
      0='0 Times';
      1='1-2 Times';
      2='3-9 Times';
      4='10+ Times';

      ")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


---
title: "HPTN 061 Initial Visit Scoring"
author: "Blaise Albis-Burdige"
date: '`r format(Sys.time(), "%B %d, %Y %r %Z")`'
output:
  html_document:
    highlight: tango
    theme: cerulean
    toc: yes
    toc_depth: 5
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, comment=NA)
```

#Setup
##Imports

```{r}
library(readr)
library(stringr)
library(dplyr)
library(knitr)
library(kableExtra)
library(table1)
library(car)
library(assertthat)

```
##Reading In Dataset
```{r}
hptn <- read_csv('hptn061WideFinalMod.csv')
```

#Demographic Information
## Birthplace given by DEMcount
```{r Birthplace, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest1 <- (hptn$DEMcount_101)




##Replace numeric code with corresponding string

 factorOfInterest1<- recode(factorOfInterest1, 
        "840 = 'USA';581='US Outlying Island';084='Belize';120='Cameroon';124='Canada';132='Cape Verde';192='Cuba';231='Ethiopia';250='France';288='Ghana';384='Ivory Coast';404='Kenya';484='Mexico';504='Morocco';566='Nigeria';686='Senegal';710='South Africa';724='Spain';780='Trinidad and Tobago';388='Other';630='Other';591='Other';800='Other';430='Other';332='Other';276='Other';52='Other';850='Other';716='Other';44='Other';324='Other';32='Other';308='Other';266='Other';214='Other';212='Other';136='Other';else=") 



n <- (table(factorOfInterest1))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Education given by DEMeduc (highest grade completed)
```{r Education, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest2 <- (hptn$DEMeduc_101)



##Replace numeric code with corresponding string

factorOfInterest2<- recode(factorOfInterest2, 
       "1 = '8th grade or equivalent or less';2='Some high school';3='High school graduate or equivalent';4='Vocational/trade/technical school';5='Some college or 2 year degree';6='Finished college';7='Masters or other advanced degree';NA='NA';else=")


n <- (table(factorOfInterest2))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Employment (DEMwork)
```{r Employment, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest4 <- (hptn$DEMwork_101)



##Replace numeric code with corresponding string

factorOfInterest4<- recode(factorOfInterest4, 
       "1 = 'Yes, working full-time';2='yes, working part-time';3='No, unemployed';4='No, retired';5='No, unable to work';NA='NA';else=")

n <- (table(factorOfInterest4))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Yearly Income (DEMincom)
```{r Income, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest3 <- (hptn$DEMincom_101)




##Replace numeric code with corresponding string

factorOfInterest3<- recode(factorOfInterest3, 
       "1 = 'Less than $5,000';2='$5,000-$9,999';3='$10,000-$19,999';4='$20,000-$29,999';5='$30,000-$39,999';6='$40,000-$49,999';7='$50,000-$59,999';8='$60,000-$69,999';9='$70,000-$79,999';10='$80,000 or more';NA='NA';else=")



n <- (table(factorOfInterest3))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


## Frequency of insufficient income support in the last 6 months  (DEMnomon)
```{r insfIncome, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest5 <- (hptn$DEMnomon_101)



##Replace numeric code with corresponding string

factorOfInterest5<- recode(factorOfInterest5, 
       "1 = 'Never';2='Once in a while';3='Fairly often';4='Very often';NA='NA';else=")


n <- (table(factorOfInterest5))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]


kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Have health coverage?(DEMhcov_101)
```{r HealthCoverage, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest6 <- (hptn$DEMhcov_101)




##Replace numeric code with corresponding string

factorOfInterest6<- recode(factorOfInterest6, 
       "1 = 'Yes';2='No';NA='NA';else=")


n <- (table(factorOfInterest6))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Description of household (DEMhouse_101)
```{r Household, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest7 <- (hptn$DEMhouse_101)





##Replace numeric code with corresponding string

factorOfInterest7<- recode(factorOfInterest7, 
       "1 = 'Living alone';2='Living with a partner or spouse (with or without children)';3='Living with a roommate or roommates (who are not partners)';4='Living with relatives';5='Living with members of my house (such as house ball community)';6='Do not have a stable home';7='Other';NA='NA';")

n <- (table(factorOfInterest7))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Where did you get your most recent HIV test?(ACTSTWH_101)
```{r recentTest, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest8 <- (hptn$ACTSTWH_101)





##Replace numeric code with corresponding string

factorOfInterest8<- recode(factorOfInterest8, 
       "1= 'HIV/AIDS street outreach program/Mobile Unit'; 
2= 'HIV counseling and testing site'; 
3= 'Needle exchange program'; 
4= 'Research site'; 
5= 'Adult HIV/AIDS or infectious disease clinic'; 
6= 'Sexually transmitted disease clinic'; 
7= 'Community health center/public health clinic/free clinic'; 
8= 'Family planning clinic'; 
9= 'Hospital outpatient clinic'; 
10= 'Emergency room'; 
11= 'Drug treatment program'; 
12= 'Private doctors office (including HMO)'; 
13= 'Correctional facility (jail or prison)'; 
14= 'Military'; 
15= 'Home health care'; 
16= 'Other';")




n <- (table(factorOfInterest8))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Why did you choose to get tested for HIV this most recent time?(AC_101)
```{r ReasonForTest, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$AC1_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      " 'SICK'= 'I was sick'; 'NOC,INC'='I did not use a condom when having sex & I was in jail, prison, or juvenile detention center';'NWSO,ADV'=  'I had just started a new relationship & Someone told me to get tested'; 'NOC,OTCR'= 'I did not use a condom when having sex & I was offered testing with other care';
'BRKC'= 'A condom broke'; 
'NOC'= 'I did not use a condom when having sex'; 
'NWSO'= 'I had just started a new relationship'; 
'INJ'= 'I used needles to inject drugs'; 
'ADV'= 'Someone told me to get tested'; 
'DKNW'= 'I did not know I was being tested'; 
'APPT'= 'It was at a routine medical appointment'; 
'PHYS'= 'I had an employee physical'; 
'BLOD'= 'I gave blood'; 
'MILT'= 'I joined the military'; 
'INC'= 'I was in jail, prison, or juvenile detention center'; 
'CLUB'= 'I saw testing at a bar or club'; 
'VAN'= 'I saw a testing program on the street (i.e. mobile van, health fair, etc.)'; 
'PRDE'= 'I saw a testing program at a pride celebration (e.g. gay pride parade, festival)'; 
'SCHL'= 'It was at a testing program in school';
'OTCR'= 'I was offered testing with other care (e.g. STD clinic, ER, community health program)';
'PAID'= 'I was provided money to get tested';'OTH'= 'Other';'NOC,NWSO'= 'I did not use a condom when having sex & I had just started a new relationship';'BRKC,NOC'= 'A condom broke';'NOC,VAN'='A condom broke'; 'NOC,OTH'='A condom broke';'NOC,APPT'='A condom broke';'NOC,ADV'='A condom broke';'NOC,NWSO,ADV'='A condom broke';else=")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##Gender Identity: Which of the following word or words do you feel best describes you today? (AC3_101)
```{r genderIdent, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$AC3_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      "'MALE'='Male';'MALE,REAL'='Male & Realness';'MALE,BTCH'='Male & Butch queen';'MALE,OTHB'='Male & Other';'MALE,FMLE'='Male & Female';'MALE,TRNS'='Male & Transsexual';'MALE,GQ'='Male & Genderqueer';'MALE,Feme'='Male & Femme queen';'MALE,REAL,BTCH'='Male & Realness & Butch queen';
      'FMLE'='Female';
      'TRNG'='Transgender';
      'TRNS'='Transsexual'; 
      'GQ'='Genderqueer';
      'REAL'='Realness';
      'BTCH'='Butch queen';
      'FEME'='Femme queen';
      'TRNY'='Trannie';
      'INTER'='Intersex';
      'CRSS'='Crossdresser';
      'OTHB'='Other'; else = 'Some other combo';
      ")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

##anySti:Any STI (any)
```{r genderIdent, echo=FALSE}


##Copy is a vector that holds the country code of each participant

factorOfInterest9 <- (hptn$inc4_101)

##Replace numeric code with corresponding string

factorOfInterest9<- recode(factorOfInterest9,
      "
      0='0 Times';
      1='1-2 Times';
      2='3-9 Times';
      4='10+ Times';

      ")


n <- (table(factorOfInterest9))
Percent <- (prop.table(n) * 100)
df <- as.data.frame(cbind(n, Percent))

df = df[rev(order(df$Percent)),]

####Remove the weird N in the last row --> What is it?

#df <- df[-nrow(df),] 

kable(df,booktabs = TRUE,
      linesep = '',
      col.names = c("n", "Percent")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```
